Enhanced proximity effect in zigzag-shaped Majorana Josephson junctions.

### 2019-02-26 paper/snakemajoranas.tex
small changes

\renewcommand{\comment}[2]{#2}
% Uncomment the following line for paragraph descriptions to appear in the file.
\renewcommand{\comment}{\paragraph}

@@

\author{Tom Laeven}
\affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
\email[Electronic address: ]{tlaeven@hotmail.com}
\author{Bas Nijholt}
\affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
\email[Electronic address: ]{bas@nijho.lt}
\author{Michael Wimmer}
\email[Electronic address: ]{m.t.wimmer@tudelft.nl}
\affiliation{Kavli Institute of Nanoscience, Delft University of Technology,
 P.O. Box 4056, 2600 GA Delft, The Netherlands}
\affiliation{QuTech, Delft University of Technology,
 P.O. Box 4056, 2600 GA Delft, The Netherlands}
\author{Anton R. Akhmerov}
\affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
\email[Electronic address: ]{zigzag@antonakhmerov.org}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=0.75\columnwidth]{figures/zigzag.pdf}
\caption{The straight (top) and the zigzag (bottom) SNS junction.
The zigzag pattern has a peak-to-peak amplitude $z_y$ and a period $z_x$.
The yellow areas are superconductors with a phase difference of $\phi$ between the top and the bottom.
The middle area is the semiconductor of width $W$.
A magnetic field $B$ pointing in the $x$-direction causes a Zeeman splitting in the semiconductor
A trajectory traveling at a grazing angle (red curve) has a very long flight time $\tau_\textrm{f}$ and a very small induced gap $E_\textrm{gap}$.
At the same time, the zigzag geometry limits the length of a trajectory therefore lowering $\tau_\textrm{f}$ and increasing $E_\textrm{gap}$.
\label{fig:setup}}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/bandstructures}
\caption{Band stuctures of the system in Fig.~\ref{fig:setup}(b) with different zigzag amplitudes.
The blue lines correspond to a trivial phase ($\phi=0$, $B=0$) and the orange lines to a topological phase ($\phi=\pi$, $B = \SI{1}{T}$).
The three subplots are for different amplitudes of the zigzag, with (a) a straight system $z_y=0$, (b) $z_y=W/2$, and (c) $z_y=W$, where $W=\SI{200}{\nm}$ is the junction width.
On the $x$-axis is the Bloch momentum where $z_x=\SI{1300}{\nm}$.
Subplot (a) has a different scale on the $x$-axis for $k_x < 0$ than the other subplots and displays the unfolded band structure.
For the right-hand side of (a) ($k_x > 0$), (b), and (c), the folding is the same, such that the velocity $v=dE/dk$ can be compared visually.
We observe that once there are no more straight trajectories inside the junction (when $z_y=W$) the spectrum becomes insensitive to the momentum $k_x$ and equivalently, $v_\textrm{F}$ decreases.
As the zigzag amplitude increases, the band gap $E_\textrm{gap}$ increases by an order of magnitude.
The combination of these ensures a significant decrease of the Majorana size because $\xi_M \propto v_\textrm{F}/E_\textrm{gap}$
The parameter values are written at the end of Sec.~\ref{sec:setup}.\label{fig:band_structures}}
\end{figure}

@@

\comment{We calculate the wave functions and find the Majorana lengths by fitting an exponential.}
We model a finite system and compute the Majorana wave function in different geometries: ribbon, zigzag, sine-like parallel curves, and a variant of the latter with disordered edges.
By diagonalizing the Hamiltonian, we find the Majorana energy $E_\textrm{M}$, and by using the corresponding eigenstate of that lowest energy, we get the wave function.
To reduce the finite size effects in determining the Majorana size $\xi_\textrm{M}$ in a zigzag system, we introduce a particle-hole symmetry breaking potential $V \sigma_0 \tau_0$ on one edge, such that one of the Majorana states is pushed away from zero energy.
We then find $\xi_\textrm{M}$ by fitting an exponential to the density of the single Majorana wave function projected on the $x$-axis.
In the straight system we use the eigenvalue decomposition of the translation operator at zero energy~\ref{nijholt2015orbital} for performance reasons.

>>>>

\renewcommand{\comment}[2]{#2}
% Uncomment the following line for paragraph descriptions to appear in the file.
% \renewcommand{\comment}{\paragraph}

@@

\author{Tom Laeven}
\email[Electronic address: ]{tlaeven@hotmail.com}
\affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
\author{Bas Nijholt}
\email[Electronic address: ]{bas@nijho.lt}
\affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}
\author{Michael Wimmer}
\email[Electronic address: ]{m.t.wimmer@tudelft.nl}
\affiliation{Kavli Institute of Nanoscience, Delft University of Technology,
 P.O. Box 4056, 2600 GA Delft, The Netherlands}
\affiliation{QuTech, Delft University of Technology,
 P.O. Box 4056, 2600 GA Delft, The Netherlands}
\author{Anton R. Akhmerov}
\email[Electronic address: ]{zigzag@antonakhmerov.org}
\affiliation{Kavli Institute of Nanoscience, Delft University of Technology, P.O. Box 4056, 2600 GA Delft, The Netherlands}

@@

\begin{figure}[!htb]
\centering
\includegraphics[width=0.9\columnwidth]{figures/zigzag.pdf}
\caption{The straight (top) and the zigzag (bottom) SNS junction.
The zigzag pattern has a peak-to-peak amplitude $z_y$ and a period $z_x$.
The yellow areas are superconductors with a phase difference of $\phi$ between the top and the bottom.
The middle area is the semiconductor of width $W$.
A magnetic field $B$ pointing in the $x$-direction causes a Zeeman splitting in the semiconductor
A trajectory traveling at a grazing angle (red curve) has a very long flight time $\tau_\textrm{f}$ and a very small induced gap $E_\textrm{gap}$.
At the same time, the zigzag geometry limits the length of a trajectory therefore lowering $\tau_\textrm{f}$ and increasing $E_\textrm{gap}$.
\label{fig:setup}}
\end{figure}

@@

\begin{figure}[!htb]
\includegraphics[width=\columnwidth]{figures/bandstructures}
\caption{Band stuctures of the system in Fig.~\ref{fig:setup}(b) with different zigzag amplitudes.
The blue lines correspond to a trivial phase ($\phi=0$, $B=0$) and the orange lines to a topological phase ($\phi=\pi$, $B = \SI{1}{T}$).
The three subplots are for different amplitudes of the zigzag, with (a) a straight system $z_y=0$, (b) $z_y=W/2$, and (c) $z_y=W$, where $W=\SI{200}{\nm}$ is the junction width.
Subplot (a) has a different $x$-scale for $k_x < 0$ from the other subplots and displays the unfolded band structure.
For the right-hand side of (a) ($k_x > 0$), (b), and (c), the folding is the same, such that the velocity $v=dE/dk$ can be compared visually.
We observe that once there are no more straight trajectories inside the junction (when $z_y=W$) the spectrum becomes insensitive to the momentum $k_x$ and equivalently, $v_\textrm{F}$ decreases.
As the zigzag amplitude increases, the band gap $E_\textrm{gap}$ increases by an order of magnitude.
The combination of these ensures a significant decrease of the Majorana size because $\xi_M \propto v_\textrm{F}/E_\textrm{gap}$
The parameter values are written at the end of Sec.~\ref{sec:setup}.\label{fig:band_structures}}
\end{figure}

@@

\comment{We calculate the wave functions and find the Majorana lengths by fitting an exponential.}
We model a finite system and compute the Majorana wave function in different geometries: ribbon, zigzag, sine-like parallel curves, and a variant of the latter with disordered edges.
By diagonalizing the Hamiltonian, we find the Majorana energy $E_\textrm{M}$, and by using the corresponding eigenstate of that lowest energy, we get the wave function.
To reduce the finite size effects in determining the Majorana size $\xi_\textrm{M}$ in a zigzag system, we introduce a particle-hole symmetry breaking potential $V \sigma_0 \tau_0$ on one edge, such that one of the Majorana states is pushed away from zero energy.
We then find $\xi_\textrm{M}$ by fitting an exponential to the density of the single Majorana wave function projected on the $x$-axis.
In the straight system we use the eigenvalue decomposition of the translation operator at zero energy~\cite{nijholt2015orbital} for performance reasons.
